### 2019-08-15 mycv/subs/papers.tex
Entries
Updates

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
    % ---------------------------------------------------------
  % ---------------------------------------------------------
  \cventry
  {H. Kim, F Barlat, Y. Lee, S. Zaman, CS Lee, \underline{Y. Jeong}$^*$}
  {\href{https://doi.org/10.1016/j.ijplas.2018.07.010}{A crystal plasticity model for describing the anisotropic hardening behavior of steel sheets during strain-path changes}}
  {International Journal of Plasticity}
  {Vol. 111 p85-106, 2018}
  {
  }

>>>>

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  % ---------------------------------------------------------
  \cventry
  {\underline{Y. Jeong}$^*$, C. N. Tom\'{e}}
  {Extension of the VPSC model to account for elasto-visco-plastic behavior using a perturbed viscoplastic approach}
  {Submitted}
  {}
  {
  }

  % ---------------------------------------------------------
  \cventry
  {S. J. Park, \underline{Y. Jeong}, C. W. Kim, J. H. Lee, S. C. Cho, S. B. Lee, S. K. Lee, D. H. Kim, H. U. Hong$^*$}
  {\href{https://doi.org/10.1016/j.msea.2019.138260}{Superior tensile fracture strength of hot isostatically pressed TiC–steel metallic composite fabricated by a novel infiltration}}
  {Materials Science and Engineering: A}
  {Vol. 764(9), 2019}
  {
  }

  % ---------------------------------------------------------
  \cventry
  {\underline{Y. Jeong}$^*$, Timo Manninen}
  {\href{10.1007/s12540-019-00292-5}{Enhancement in viscoplastic self-consistent FLD prediction model and its application for austenitic and ferritic stainless steels}}
  {Metals and Materials International}
  {In Press}
  {
  }

  % ---------------------------------------------------------
  \cventry
  {H. Kim, F Barlat, Y. Lee, S. Zaman, CS Lee, \underline{Y. Jeong}$^*$}
  {\href{https://doi.org/10.1016/j.ijplas.2018.07.010}{A crystal plasticity model for describing the anisotropic hardening behavior of steel sheets during strain-path changes}}
  {International Journal of Plasticity}
  {Vol. 111 p85-106, 2018}
  {
  }
